---
title: "Holothuria tubulosa and H. forskali in co-culture with sea bass"
author: "Frank DAVID"
date: '2024-12-15'
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setlocale("LC_TIME", "C")
```

### R Markdown

This R Markdown document is made to support the findings of the paper "Biochemical signatures of Holothuria tubulosa and Holothuria forskali (Echinodermata) in co-culture with sea bass in the Frioul Islands (France)" by David et al. (2025). 


## Preparing the toolbox

Let's begin by loading the libraries that we will require to run the analyses.

```{r echo=TRUE, message=FALSE}
library(agricolae)
library(vegan)
library(ade4)
library(factoextra)
```


## Loading the data
We load growth, fatty acid and stable isotope data from the GitHub server.

For details on line and column headings please check the readme file.

```{r}

growth <- read.csv("https://raw.githubusercontent.com/DAVID-Fk/Sea-cucumber-frioul/main/WeightFrioul.csv", sep=";", header=T)
FA <- read.csv("https://raw.githubusercontent.com/DAVID-Fk/Sea-cucumber-frioul/main/FAFrioul.csv", sep=";", header=T)
SI <- read.csv("https://raw.githubusercontent.com/DAVID-Fk/Sea-cucumber-frioul/main/SIFrioul.csv", sep=";", header=T)

```

## Growth and survival

```{r}
### Let's split the dataset
  
pi=split(growth, growth$Date)$`16/11/21`
pf=split(growth, growth$Date)$`11/10/22`
  
iweight=split(pi$Mass, paste(pi$Exp, pi$Sp))
fweight=split(pf$Mass, paste(pf$Exp, pf$Sp))
    	
### Let's build a synthetic table
    	
tab1=matrix(data=NA, nrow=length(iweight), ncol=9, dimnames=list(names(iweight), c("Wi mean", "Wi sd", "Wf mean", "Wf sd", "wilcox.test", "SGR", "GR", "RWG", "Survival")))

for (i in 1:length(iweight)) {
  	tab1[i, 1]=mean(iweight[[i]])
  	tab1[i, 2]=sd(iweight[[i]])
    tab1[i, 3]=mean(fweight[[i]])
  	tab1[i, 4]=sd(fweight[[i]])  	
  	tab1[i, 5]=round(wilcox.test(iweight[[i]], fweight[[i]])$p.value, 3)
  	tab1[i, 6]=round(log(mean(fweight[[i]])/mean(iweight[[i]]))/329*100, 3)
  	tab1[i, 7]=round((mean(fweight[[i]])-mean(iweight[[i]]))/329, 3)
  	tab1[i, 8]=round((mean(fweight[[i]])-mean(iweight[[i]]))/mean(iweight[[i]])*100, 2)
  	tab1[i, 9]=round(length(fweight[[i]])/12*100, 1)
  	}
  	

```

## Fatty acids

```{r}
allFA=FA[-1,-c(1:4, which(colnames(FA)=="C23.0"))]
rownames(allFA)=FA[-1,1]
allFA[is.na(allFA)]=0

## Percentage table
prct=allFA/rowSums(allFA)*100

## Concentrations table 
conc=allFA/FA[-1,which(colnames(FA)=="C23.0")]*FA[-1,which(colnames(FA)=="StdC23")]/FA[-1,which(colnames(FA)=="Splmass")]
conctot=rowSums(conc)

### Let's compare total concentrations

a=conctot[substring(names(conctot), 1, 2)=="MF"]
b=substring(names(conctot), 8, 10)[substring(names(conctot), 1, 2)=="MF"]
waerden.test(a, b, console=T)

```

### Summary of sediments

```{r}
# Let's isolate sediment data

sed=split(prct, substring(rownames(prct), 1, 2))$Se
colMeans(sed)
sedPr=sed[, colMeans(sed)>0.6]/rowSums(sed[, colMeans(sed)>0.6])*100
  
sedconc=split(conc, substring(rownames(conc), 1, 2))$Se[, colMeans(sed)>0.6]
sedconctot=rowSums(sedconc)
waerden.test(sedconctot, substring(names(sedconctot), 8, 10), console=T)

# Let's edit a summary table
  
summarySed=data.frame(M=aggregate(cbind(sedPr, sedconctot) , by=list(substring(names(sedconctot), 8, 10)), mean), SD=aggregate(cbind(sedPr, sedconctot), by=list(substring(names(sedconctot), 8, 10)),sd), LE=aggregate(cbind(sedPr, sedconctot), by=list(substring(names(sedconctot), 8, 10)),length))

  
```

### Graphical representation

```{r echo=FALSE, fig.width=7.5, fig.height=6, fig.align="center"}

#svg(file="Fig2.svg", width=7.5, height=6)

par(las=1, mar=c(2,2,1,2), bty="n", mfrow=c(1,1))


acp=dudi.pca(sedPr, scannf = FALSE, nf = 2)
varPCA=get_pca_var(acp)
varPCAhigh=which(varPCA$contrib[,1]>100/nrow(varPCA$contrib)*1.2|varPCA$contrib[,2]>100/nrow(varPCA$contrib)*1.2)
varPCAlow=which(varPCA$contrib[,1]<100/nrow(varPCA$contrib)*1.2&varPCA$contrib[,2]<100/nrow(varPCA$contrib)*1.2)


plot(acp$li[,c(1,2)], acp$co[,c(1,2)], type="n", ann=F, bty="n", axes=F, ylim=c(-5, 5), xlim=c(-6, 6))
axis(1, pos=0, at=c(seq(-5, 5)[-6]), labels=c(seq(-5, 5)[-6]), tck=0.01, padj=-4)
axis(2, pos=0, at=c(seq(-5, 5)[-6]), labels=c(seq(-5, 5)[-6]), tck=0.01, hadj=0.1)
  

title(xlab=paste("PC1 (", round((acp$eig/sum(acp$eig)*100)[1], 1), "%)", sep=""), line=0)
title(ylab=paste("PC2 (", round((acp$eig/sum(acp$eig)*100)[2], 1), "%)", sep=""), line=0)

arrows(x0=0, y0=0, x1=acp$co[,1][varPCAhigh]*5, y1=acp$co[,2][varPCAhigh]*5, length=0.1, col="grey40", lty=5)
text(acp$co[varPCAhigh,]*5.4, labels=colnames(sedPr)[varPCAhigh], col="grey40")

arrows(x0=0, y0=0, x1=acp$co[,1][varPCAlow]*5, y1=acp$co[,2][varPCAlow]*5, length=0.1, col="grey90", lty=5)
text(acp$co[varPCAlow,]*5.4, labels=colnames(sedPr)[varPCAlow], col="grey90")

a=ordihull(acp$li, groups=substring(rownames(acp$li), 8, 10), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)

points(acp$li[, 1], acp$li[, 2], pch=23, col="grey40", bg="grey80", cex=1.5)

centroid=t(summary(a))
labs=rownames(centroid)

rect(xright=centroid[,1]+0.3, ybottom=centroid[,2]-0.4, xleft=centroid[,1]-0.3, ytop=centroid[,2]+0.4, col=adjustcolor("white", alpha=0.8), border="grey")
text(centroid, labels=labs, font=2)
  
legend("bottomright", legend=paste("n =", nrow(acp$li)), bty="n", pt.cex=2)

#dev.off()

  
```

Note that the figure was further modified with a vectorial graphics editor to avoid labels superposition

### Summary of sea cucumbers
 
```{r}

# Let's isolate sea cucumbers data

seacu=prct[-c(which(substring(rownames(prct), 1, 2)=="Se")),]
totFA=rowSums(conc[-c(which(substring(rownames(prct), 1, 2)=="Se")),])

# Let's define categories of FA
  
brFA=rowSums(seacu[, c(which(colnames(seacu)=="C15.0iso"), which(colnames(seacu)=="C15.0anteiso"), which(colnames(seacu)=="C16.0iso"))])
SFA=rowSums(seacu[, c(which(colnames(seacu)=="C14.0"), which(colnames(seacu)=="C15.0"), which(colnames(seacu)=="C16.0"), which(colnames(seacu)=="C18.0"), which(colnames(seacu)=="C19.0"),which(colnames(seacu)=="C20.0"), which(colnames(seacu)=="C21.0"), which(colnames(seacu)=="C22.0"), which(colnames(seacu)=="C24.0"))])
PUFA=rowSums(seacu[, c(which(colnames(seacu)=="C18.2w6"), which(colnames(seacu)=="C18.3w3"), which(colnames(seacu)=="C18.4w3"), which(colnames(seacu)=="C20.2w6"), which(colnames(seacu)=="C20.4w6"), which(colnames(seacu)=="C20.5w3"), which(colnames(seacu)=="C22.5w6"), which(colnames(seacu)=="C22.6w3"))])
HUFA=rowSums(seacu[, c(which(colnames(seacu)=="C20.4w6"), which(colnames(seacu)=="C20.5w3"), which(colnames(seacu)=="C22.5w6"), which(colnames(seacu)=="C22.6w3"))])
w3=rowSums(seacu[, c(which(colnames(seacu)=="C18.3w3"), which(colnames(seacu)=="C18.4w3"), which(colnames(seacu)=="C20.5w3"), which(colnames(seacu)=="C22.6w3"))])
w6=rowSums(seacu[, c(which(colnames(seacu)=="C18.2w6"), which(colnames(seacu)=="C20.2w6"), which(colnames(seacu)=="C20.4w6"), which(colnames(seacu)=="C22.5w6"))], na.rm=T)
LCMUFA=rowSums(seacu[, c(which(colnames(seacu)=="C20.1w9"), which(colnames(seacu)=="C20.1w7"), which(colnames(seacu)=="C22.1w11"), which(colnames(seacu)=="C22.1w9"), which(colnames(seacu)=="C23.1w9"), which(colnames(seacu)=="C24.1w9"))])
MUFA=rowSums(seacu[, c(which(colnames(seacu)=="C16.1w7"), which(colnames(seacu)=="C18.1w9"), which(colnames(seacu)=="C18.1w7"), which(colnames(seacu)=="C20.1w9"), which(colnames(seacu)=="C20.1w7"), which(colnames(seacu)=="C22.1w11"), which(colnames(seacu)=="C22.1w9"), which(colnames(seacu)=="C23.1w9"), which(colnames(seacu)=="C24.1w9"))])

# Let's edit a summary table

summaryFA=data.frame(M=aggregate(cbind(seacu, brFA, SFA, MUFA, LCMUFA, PUFA, HUFA, w3, w6, totFA) , by=list(substring(rownames(seacu), 1, 2)), mean), SD=aggregate(cbind(seacu, brFA, SFA, MUFA, LCMUFA, PUFA, HUFA, w3, w6, totFA), by=list(substring(rownames(seacu), 1, 2)),sd), LE=aggregate(cbind(seacu, brFA, SFA, MUFA, LCMUFA, PUFA, HUFA, w3, w6, totFA), by=list(substring(rownames(seacu), 1, 2)),length))

```


### Principal Component Analysis of fatty acid compositions of sea cucumbers
#### Holothuria tubulosa

```{r, echo=FALSE, fig.width=7.5, fig.height=12, fig.align="center"}

#svg(file="Fig3.svg", width=7.5, height=12)
  
par(las=1, mar=c(2,2,2,2), bty="n", mfrow=c(2,1), oma=c(0,0,2,0))

### Part a

  acp=dudi.pca(seacu[which(substring(rownames(seacu), 1, 2)=="HT"),], scannf = F, nf = 2, center=T, scale=T)
  varPCA=get_pca_var(acp)
  varPCAhigh=which(varPCA$contrib[,1]>100/nrow(varPCA$contrib)*1.8|varPCA$contrib[,2]>100/nrow(varPCA$contrib)*1.8)
  varPCAlow=which(varPCA$contrib[,1]<100/nrow(varPCA$contrib)*1.8&varPCA$contrib[,2]<100/nrow(varPCA$contrib)*1.8)


  plot(acp$li[,c(1,2)], acp$co[,c(1,2)], type="n", ann=F, bty="n", axes=F, xlim=c(-8,7), ylim=c(-5,5))
  axis(1, pos=0, at=c(seq(-7, 7)[-8]), labels=c(seq(-7, 7)[-8]), tck=0.01, padj=-4)
  axis(2, pos=0, at=c(seq(-5, 5)[-6]), labels=c(seq(-5, 5)[-6]), tck=0.01, hadj=-0.1)

  title(main=expression(bolditalic("Holothuria tubulosa")), line=1, cex.main=2)
  title(xlab=paste("PC1 (", round((acp$eig/sum(acp$eig)*100)[1], 1), "%)", sep=""), line=0)
  title(ylab=paste("PC2 (", round((acp$eig/sum(acp$eig)*100)[2], 1), "%)", sep=""), line=0)
  
# Note that the graphic is inversed to better highlight similarities with body wall data

  arrows(x0=0, y0=0, x1=-acp$co[,1][varPCAhigh]*6, y1=-acp$co[,2][varPCAhigh]*6, length=0.1, col="grey40", lty=5)
  text(-acp$co[,1][varPCAhigh]*6.8, -acp$co[,2][varPCAhigh]*6.8, labels=names(varPCAhigh), col="grey40")
  
  arrows(x0=0, y0=0, x1=-acp$co[,1][varPCAlow]*6, y1=-acp$co[,2][varPCAlow]*6, length=0.1, col="grey90", lty=5)
  text(-acp$co[,1][varPCAlow]*6.8, -acp$co[,2][varPCAlow]*6.8, labels=names(varPCAlow), col="grey90")

  a=ordihull(-acp$li, groups=substring(rownames(acp$li), 8, 10), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
  points(-acp$li[, 1], -acp$li[, 2], pch=21, col="grey40", bg="grey80", cex=1.5)

  centroid=t(summary(a))
  labs=rownames(centroid)

  rect(xright=centroid[,1]+0.5, ybottom=centroid[,2]-0.4, xleft=centroid[,1]-0.5, ytop=centroid[,2]+0.4, col=adjustcolor("white", alpha=0.8), border="grey")
  text(centroid, labels=c("E2", "E1", "E3", "C", "Wo", "Wi"), font=2)
  legend("topright", legend=expression(bold("a")), bty="n", cex=3.5, inset=c(0, -0.1))
  legend("topleft", legend=c("Body wall"), pch=21, col="grey40", text.col="black", pt.bg="grey80", bty="n", pt.cex=2, inset=c(0.02, 0))
  legend("bottomright", legend=paste("n =", nrow(acp$li)), bty="n", pt.cex=2)
  
  ### Part b
  
  acp=dudi.pca(seacu[which(substring(rownames(seacu), 1, 2)=="MT"),], scannf = F, nf = 2, center=T, scale=T)
  varPCA=get_pca_var(acp)
  varPCAhigh=which(varPCA$contrib[,1]>100/nrow(varPCA$contrib)*1.8|varPCA$contrib[,2]>100/nrow(varPCA$contrib)*1.8)
  varPCAlow=which(varPCA$contrib[,1]<100/nrow(varPCA$contrib)*1.8&varPCA$contrib[,2]<100/nrow(varPCA$contrib)*1.8)

  
  plot(acp$li[,c(1,2)], acp$co[,c(1,2)], type="n", ann=F, bty="n", axes=F, xlim=c(-8,7), ylim=c(-5,5))
  axis(1, pos=0, at=c(seq(-7, 7)[-8]), labels=c(seq(-7, 7)[-8]), tck=0.01, padj=-4)
  axis(2, pos=0, at=c(seq(-5, 5)[-6]), labels=c(seq(-5, 5)[-6]), tck=0.01, hadj=-0.1)

  title(xlab=paste("PC1 (", round((acp$eig/sum(acp$eig)*100)[1], 1), "%)", sep=""), line=0)
  title(ylab=paste("PC2 (", round((acp$eig/sum(acp$eig)*100)[2], 1), "%)", sep=""), line=0)
  
  arrows(x0=0, y0=0, x1=acp$co[,1][varPCAhigh]*6, y1=acp$co[,2][varPCAhigh]*6, length=0.1, col="grey40", lty=5)
  text(acp$co[,1][varPCAhigh]*6.8, acp$co[,2][varPCAhigh]*6.8, labels=names(varPCAhigh), col="grey40")

  arrows(x0=0, y0=0, x1=acp$co[,1][varPCAlow]*6, y1=acp$co[,2][varPCAlow]*6, length=0.1, col="grey90", lty=5)
  text(acp$co[,1][varPCAlow]*6.8, acp$co[,2][varPCAlow]*6.8, labels=names(varPCAlow), col="grey90")
  
a=ordihull(acp$li, groups=substring(rownames(acp$li), 8, 10), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
  points(acp$li[, 1], acp$li[, 2], pch=22, col="grey40", bg="grey80", cex=1.5)

  centroid=t(summary(a))
  labs=rownames(centroid)

  rect(xright=centroid[,1]+0.5, ybottom=centroid[,2]-0.4, xleft=centroid[,1]-0.5, ytop=centroid[,2]+0.4, col=adjustcolor("white", alpha=0.8), border="grey")
  text(centroid, labels=c("E2", "E1", "E3", "C", "Wo", "Wi"), font=2)
  legend("topright", legend=expression(bold("b")), bty="n", cex=3.5, inset=c(0, -0.1))
  legend("topleft", legend=c("Muscle bands"), pch=22, col="grey40", text.col="black", pt.bg="grey80", bty="n", pt.cex=2, inset=c(0.02, 0))
  legend("bottomright", legend=paste("n =", nrow(acp$li)), bty="n", pt.cex=2)

#dev.off()


```

Note that the figure was further modified with a vectorial graphics editor to avoid labels superposition

#### Holothuria forskali

```{r, echo=FALSE, fig.width=7.5, fig.height=12, fig.align="center"}

#svg(file="Fig4.svg", width=7.5, height=12)
  
par(las=1, mar=c(2,2,2,2), bty="n", mfrow=c(2,1), oma=c(0,0,2,0))

### Part a

  acp=dudi.pca(seacu[which(substring(rownames(seacu), 1, 2)=="BF"),], scannf = F, nf = 2, center=T, scale=T)
  varPCA=get_pca_var(acp)
  varPCAhigh=which(varPCA$contrib[,1]>100/nrow(varPCA$contrib)*1.8|varPCA$contrib[,2]>100/nrow(varPCA$contrib)*1.8)
    varPCAlow=which(varPCA$contrib[,1]<100/nrow(varPCA$contrib)*1.8&varPCA$contrib[,2]<100/nrow(varPCA$contrib)*1.8)

  
  plot(acp$li[,c(1,2)], acp$co[,c(1,2)], type="n", ann=F, bty="n", axes=F, xlim=c(-8,7), ylim=c(-6,5))
  axis(1, pos=0, at=c(seq(-8, 7)[-9]), labels=c(seq(-8, 7)[-9]), tck=0.01, padj=-4)
  axis(2, pos=0, at=c(seq(-6, 5)[-7]), labels=c(seq(-6, 5)[-7]), tck=0.01, hadj=-0.1)

  title(main=expression(bolditalic("Holothuria forskali")), line=1, cex.main=2)
  title(xlab=paste("PC1 (", round((acp$eig/sum(acp$eig)*100)[1], 1), "%)", sep=""), line=0)
  title(ylab=paste("PC2 (", round((acp$eig/sum(acp$eig)*100)[2], 1), "%)", sep=""), line=0)
  
  arrows(x0=0, y0=0, x1=acp$co[,1][varPCAhigh]*6, y1=acp$co[,2][varPCAhigh]*6, length=0.1, col="grey40", lty=5)
  text(acp$co[,1][varPCAhigh]*6.8, acp$co[,2][varPCAhigh]*6.8, labels=names(varPCAhigh), col="grey40")

  arrows(x0=0, y0=0, x1=-acp$co[,1][varPCAlow]*6, y1=-acp$co[,2][varPCAlow]*6, length=0.1, col="grey90", lty=5)
  text(-acp$co[,1][varPCAlow]*6.8, -acp$co[,2][varPCAlow]*6.8, labels=names(varPCAlow), col="grey90")

  a=ordihull(acp$li, groups=substring(rownames(acp$li), 8, 10), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
  points(acp$li[, 1], acp$li[, 2], pch=21, col="grey40", bg="grey20", cex=1.5)

  centroid=t(summary(a))
  labs=rownames(centroid)

  rect(xright=centroid[,1]+0.5, ybottom=centroid[,2]-0.4, xleft=centroid[,1]-0.5, ytop=centroid[,2]+0.4, col=adjustcolor("white", alpha=0.8), border="grey")
  text(centroid, labels=c("E2", "E1", "E3", "C", "Wo", "Wi"), font=2)
  legend("topright", legend=expression(bold("a")), bty="n", cex=3.5, inset=c(0, -0.1))
  legend("topleft", legend=c("Body wall"), pch=21, col="grey40", text.col="black", pt.bg="grey20", bty="n", pt.cex=2, inset=c(0.02, 0))
  legend("bottomright", legend=paste("n =", nrow(acp$li)), bty="n", pt.cex=2)
  
  ### Part b
  
  acp=dudi.pca(seacu[which(substring(rownames(seacu), 1, 2)=="MF"),], scannf = F, nf = 2, center=T, scale=T)
  varPCA=get_pca_var(acp)
  varPCAhigh=which(varPCA$contrib[,1]>100/nrow(varPCA$contrib)*1.8|varPCA$contrib[,2]>100/nrow(varPCA$contrib)*1.8)
  varPCAlow=which(varPCA$contrib[,1]<100/nrow(varPCA$contrib)*1.8&varPCA$contrib[,2]<100/nrow(varPCA$contrib)*1.8)

  
  plot(acp$li[,c(1,2)], acp$co[,c(1,2)], type="n", ann=F, bty="n", axes=F, xlim=c(-8,7), ylim=c(-6,5))
  axis(1, pos=0, at=c(seq(-8, 7)[-9]), labels=c(seq(-8, 7)[-9]), tck=0.01, padj=-4)
  axis(2, pos=0, at=c(seq(-6, 5)[-7]), labels=c(seq(-6, 5)[-7]), tck=0.01, hadj=-0.1)

  title(xlab=paste("PC1 (", round((acp$eig/sum(acp$eig)*100)[1], 1), "%)", sep=""), line=0)
  title(ylab=paste("PC2 (", round((acp$eig/sum(acp$eig)*100)[2], 1), "%)", sep=""), line=0)
  
# Note that the graphic is inversed to better highlight similarities with body wall data

  arrows(x0=0, y0=0, x1=acp$co[,1][varPCAhigh]*6, y1=-acp$co[,2][varPCAhigh]*6, length=0.1, col="grey40", lty=5)
  text(acp$co[,1][varPCAhigh]*6.8, -acp$co[,2][varPCAhigh]*6.8, labels=names(varPCAhigh), col="grey40")

  arrows(x0=0, y0=0, x1=acp$co[,1][varPCAlow]*6, y1=acp$co[,2][varPCAlow]*6, length=0.1, col="grey90", lty=5)
  text(acp$co[,1][varPCAlow]*6.8, acp$co[,2][varPCAlow]*6.8, labels=names(varPCAlow), col="grey90")
  
  a=ordihull(cbind(acp$li[, 1], -acp$li[, 2]), groups=substring(rownames(acp$li), 8, 10), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
  points(acp$li[, 1], -acp$li[, 2], pch=22, col="grey40", bg="grey20", cex=1.5)

  centroid=t(summary(a))
  labs=rownames(centroid)

  rect(xright=centroid[,1]+0.5, ybottom=centroid[,2]-0.4, xleft=centroid[,1]-0.5, ytop=centroid[,2]+0.4, col=adjustcolor("white", alpha=0.8), border="grey")
  text(centroid, labels=c("E2", "E1", "E3", "C", "Wo", "Wi"), font=2)
  legend("topright", legend=expression(bold("b")), bty="n", cex=3.5, inset=c(0, -0.1))
  legend("topleft", legend=c("Muscle bands"), pch=22, col="grey40", text.col="black", pt.bg="grey20", bty="n", pt.cex=2, inset=c(0.02, 0))
  legend("bottomright", legend=paste("n =", nrow(acp$li)), bty="n", pt.cex=2)

#dev.off()

```

Note that the figure was further modified with a vectorial graphics editor to avoid labels superposition

## Stable isotopes
### Graphical representation (biplot 13C-15N)

```{r echo=FALSE, fig.width=7.5, fig.height=12, fig.align="center"}

#pdf(file="Fig5.pdf", width=7.5, height=12)

par(las=1, mar=c(5,5,2,2), bty="n", mfrow=c(2,1), oma=c(0,0,2,0), cex.lab=1.5)

### Part a

Htu=SI[c(which(substring(SI$Id, 2, 2)=="T")),]

plot(Htu$X13C, Htu$X15N, bty="n", xlim=c(-24,-12), ylim=c(4, 12), xlab=expression(paste(delta^13, "C")), ylab=expression(paste(delta^15, "N")), type="n")

title(main=expression(bolditalic("Holothuria tubulosa")), line=1, cex.main=2)
  
a=ordihull(cbind(Htu$X13C, Htu$X15N), groups=paste(substring(Htu$Exp, 1, 2), substring(Htu$Id, 1, 2)), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
points(Htu$X13C, Htu$X15N,pch=c(21, 22)[as.factor(substring(Htu$Id, 1, 2))], bg="grey80", col="grey40", cex=1.5)
points(SI$X13C[c(which(substring(SI$Id, 1, 1)=="F"))], SI$X15N[c(which(substring(SI$Id, 1, 1)=="F"))], pch=c(8, 8, 3, 8, 8, 8, 3), cex=1.5)

centroid=t(summary(a))
rect(xright=centroid[,1]+0.45, ybottom=centroid[,2]-0.35, xleft=centroid[,1]-0.45, ytop=centroid[,2]+0.35, col=adjustcolor("white", alpha=0.7), border="grey")
text(centroid, labels=c("C", "C", "E1", "E1", "E2", "E2", "E3", "E3", "Wi", "Wi", "Wo", "Wo"), font=2)
  
legend("topright", legend=expression(bold("a")), bty="n", cex=3.5, inset=c(0, -0.1))

legend("topleft", legend=c("Body wall", "Muscle bands", "Feed", "Fish faeces"), pch=c(21, 22, 3, 8), col="grey40", text.col="black", pt.bg="grey80", bty="n", pt.cex=2, inset=c(0.03, 0.01))

legend("bottomright", legend=paste("n =", nrow(SI[-c(which(substring(SI$Id, 2, 2)=="F")),])), bty="n", pt.cex=2)


### Part b

Hfo=SI[c(which(substring(SI$Id, 2, 2)=="F")),]

plot(Hfo$X13C, Hfo$X15N, bty="n", xlim=c(-24,-12), ylim=c(4, 12), xlab=expression(paste(delta^13, "C")), ylab=expression(paste(delta^15, "N")), type="n")

title(main=expression(bolditalic("Holothuria forskali")), line=1, cex.main=2)
  
a=ordihull(cbind(Hfo$X13C, Hfo$X15N), groups=paste(substring(Hfo$Exp, 1, 2), substring(Hfo$Id, 1, 2)), lty=4, label=F, display=c("sites"), draw="polygon", col="white", alpha=200)
points(Hfo$X13C, Hfo$X15N,pch=c(21, 22)[as.factor(substring(Hfo$Id, 1, 2))], bg="grey20", col="grey40", cex=1.5)
points(SI$X13C[c(which(substring(SI$Id, 1, 1)=="F"))], SI$X15N[c(which(substring(SI$Id, 1, 1)=="F"))], pch=c(8, 8, 3, 8, 8, 8, 3), cex=1.5)

centroid=t(summary(a))
rect(xright=centroid[,1]+0.45, ybottom=centroid[,2]-0.35, xleft=centroid[,1]-0.45, ytop=centroid[,2]+0.35, col=adjustcolor("white", alpha=0.7), border="grey")
text(centroid, labels=c("C", "C", "E1", "E1", "E2", "E2", "E3", "E3", "Wi", "Wi", "Wo", "Wo"), font=2)
  
legend("topright", legend=expression(bold("b")), bty="n", cex=3.5, inset=c(0, -0.1))

legend("topleft", legend=c("Body wall", "Muscle bands", "Feed", "Fish faeces"), pch=c(21, 22, 3, 8), col="grey40", text.col="black", pt.bg="grey20", bty="n", pt.cex=2, inset=c(0.03, 0.01))

legend("bottomright", legend=paste("n =", nrow(SI[-c(which(substring(SI$Id, 2, 2)=="T")),])), bty="n", pt.cex=2)


#dev.off()
  
```